### 2018-07-21 paper/design.tex

Finally, we describe the complete \ac{SPORES} protocol (\cref{SPORES}).
\Ac{SPORES} adds an e-squad protocol to \ac{SPOR}.
This protocol provides provides each device in the e-squad of a user with 
prediction of its own and the other devices' availability.
This availability can then be used by the devices in the e-squad to participate 
as nodes for the routing of \ac{SPOR}, \ie making it \iac{P2P} system (network 
structure).

\Ac{SPORES} also allows the e-squad to act as one autonomous system, rather 
than several.
In particular, the devices will exchange information so that one device can 
receive an expected message on the behalf of another device, \eg while it is 
offline.

>>>>

A device's availability depends on its user's behaviour, hence the device must 
predict this behaviour.
This is best done jointly between the user's all devices.
In \cref{sec:squad_overlay}, we describe a protocol which allows the devices to 
compute their own availability prediction function based on the observations by 
all other devices.

Finally, we describe the complete \ac{SPORES} protocol (\cref{SPORES}), which 
allows the device squad to act as an autonomous system.
In particular, we introduce a protocol which allows transferring larger 
messages by fragmentation and reassembly across the devices in the squad.

### 2018-07-21 paper/file-exchange-design.tex
Adapts the design intro to reflect changes in the subsections

\subsection{Transferring files over \acs{SPORES}}%
\label{sec:file_exchange}

So far, we have treated the case where Alice sends \emph{one} message to Bob in 
\emph{one} round and any one of Bob's devices receives it.
Now we will consider a slightly different scenario, we will show how to build a 
file transferring service on top of \ac{SPORES}.
Consider that the message \(m\) that Alice wants to send to Bob is too large to 
successfully pass every layer of the route.
\Eg each device goes offline and back online every \(t\) time units, the 
bandwidth is \(w\) size units per time unit and the message is \(l\) size 
units; if \(l\geq t w\), then the message \(m\) can never be delivered as any 
device will go offline before relaying it to the next node.
The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, m_n\), 
where \(l/n\leq w t\).
The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
different devices.
In this section we describe two things:
first, the protocol run by the devices in Alice's and Bob's device squads to 
compute the function \(\avail\);
second, the protocol for reassembling a split message where the parts are 
received by different devices.

>>>>

\subsection{\acs{SPORES}: fragmentation and reassembly across devices}%
\label{SPORES}%
\label{sec:file_exchange}

So far, we have treated the case where Alice sends \emph{one} message to Bob in 
\emph{one} round and any one of Bob's devices receives it.
Now we will consider a slightly different scenario, we will show how to build a 
file transferring service on top of \ac{SPORES}.
Consider that the message \(m\) that Alice wants to send to Bob is too large to 
successfully pass every layer of the route.
\Eg each device goes offline and back online every \(t\) time units, the 
bandwidth is \(w\) size units per time unit and the message is \(l\) size 
units; if \(l\geq t w\), then the message \(m\) can never be delivered as any 
device will go offline before relaying it to the next node.
The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, m_n\), 
where \(l/n\leq w t\).
The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
different devices.
In this section we describe a protocol for reassembling a split message where 
the parts are received by different devices of the e-squad.

\commentDaniel{I leave it to Adrien, for now, to write this up.}

### 2018-07-21 paper/sphinxes.tex
Adds comment to figure concerning issue #42
Drops POR as scheme in favour of Sphinxes
Moves \New* statements to preamble to fix weird bug
Clarifies what "algorithm fails" means

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security.
Sphinx only provides one node per onion layer, in this section we extend Sphinx 
to Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)

\begin{figure}
  \includegraphics[width=\linewidth]{figures/OR-POR.png}
  \caption{\label{fig:OR-POR}%
    Illustration of the conceptual difference between traditional onion routing 
    and mixing (top) and \ac{POR} (bottom).
  }
\end{figure}

@@

\NewVariable{\sk}{x}
\NewVariable{\pk}{X}

@@

\NewAlgorithm{\Enc}{Enc}

@@

\NewScheme{\Sphinxes}{POR}
\NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
\NewAlgorithm{\CreateFwd}{\Sphinxes[CreateForward]}
\NewAlgorithm{\CreateReply}{\Sphinxes[CreateReply]}
\NewAlgorithm{\UseReply}{\Sphinxes[UseReply]}
\NewAlgorithm{\ProcessHeader}{\Sphinxes[ProcessHeader]}

@@

\NewVariable{\G}{\mathcal{G}}
\NewVariable*{\mac}{\mu}
\NewVariable*{\prg}{\rho}
\NewVariable*{\prp}{\pi}
\NewVariable{\hash}{h}
%\NewVariable{\tag}{\tau}
\NewVariable{\secret}{s}
\NewVariable{\blind}{b}
\NewVariable{\N}{\mathcal{N}}
\NewVariable{\D}{\mathcal{D}}
\NewVariable*{\nullnode}{\varepsilon}
\NewVariable{\rdvnode}{*}

@@

\NewAlgorithm{\ComputeKeys}{ComputeKeys}
\NewAlgorithm{\ComputePadding}{ComputePadding}

@@

\NewVariable{\ProcessMessage}{ProcessMessage}

@@

Otherwise. \(\beta'\) should be forwarded to \(L'\).
Compute the blinding factor \(b\gets \hash_\blind(\alpha, s_i)\) and let 
\(\alpha'\gets \alpha^b\).
Choose a node \(n\rgets L'\) uniformly at random.
Send \((\alpha', C', \beta', \gamma')\) to \(n\).
If sending to \(n\) fails, choose another node from \(L'\) uniformly at random.
If all nodes in \(L'\) fails, the algorithm fails.

>>>>

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security.
Sphinx only provides one node per onion layer, in this section we extend Sphinx 
to Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)
As such, Sphinxes could be described as a bounded random-walk protocol, \ie the 
each node selects the next node from a set restricted by the source.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/OR-POR.png}
  \caption{\label{fig:OR-POR}%
    Illustration of the conceptual difference between traditional onion routing 
    and mixing (top) and \ac{POR} (bottom).
    %\commentDaniel{This figure should be fixed, issue \#42.}
  }
\end{figure}

@@

@@

@@

@@

@@

@@

@@

Otherwise. \(\beta'\) should be forwarded to \(L'\).
Compute the blinding factor \(b\gets \hash_\blind(\alpha, s_i)\) and let 
\(\alpha'\gets \alpha^b\).
Choose a node \(n\rgets L'\) uniformly at random.
Send \((\alpha', C', \beta', \gamma')\) to \(n\).
If sending to \(n\) fails, choose another node from \(L'\) uniformly at random.
If all nodes in \(L'\) fails, the algorithm drops the packet and silently 
fails.

### 2018-07-21 paper/squad-overlay-design.tex

\subsection{The \squad Overlay} 
\label{sec:squad_overlay}

At the root of \name is predictive routing, based on the concept of Probabilistic Onion Routes (POR).
To create PORs, as a device's availability strongly depends on the activity of its owner,
 a user's devices (her \squad) must predict the future behavior of their owner. 
However, one device, belonging to an \squad, can only predict its probability to stay online in the near future
if it has a global knowledge of the user behavior over the other devices of the \squad it belongs to.
To reach this aim, \name relies on a overlay, named thereafter the \squad overlay, to share the user's behavior among devices of its \squad.

>>>>

\subsection{Predicting device availability}
\label{sec:squad_overlay}

A device's availability depends on its user.
To predict a device's availability, we must predict its user's behaviour.
A device, belonging to an \squad, can only predict its probability to stay 
online in the near future if it has global knowledge of the user behaviour over 
the other devices of the user's \squad.
We will now describe a protocol which is run by the devices in the squad which 
allows each device to compute the availability prediction function, \(\avail\).

\commentDaniel{I leave it to Adrien to write this up.
  The old stuff is commented out below.}

\endinput
